Peer influences in air travel behavior: A social autoregressive analysis

### 2015-03-27 article.Rmd
Added mathematical descriptions of matrices.

Candidate Weighting Schema
-----------------------------------------
The social network data we retrieved from Facebook allow us to construct four
social weights matrices, which we describe in this section. To aid this
presentation, we must first establish some basic notation following elementary
set theory. The set of friends of an individual  is defined as . The cardinality
of this set is the number of friends, so therefore the quantity  represents the
number of friends that individuals  and  have in common.
```{r connections_frame}
friend_connections <- tbl_df(expand.grid(id_i = user$id, id_j = user$id)) %>%
  group_by(id_i, id_j)
```

@@

friend_connections <- friend_connections %>%
  mutate(direct = check_friends(id_i, id_j, user, friends))
```
**Mutual Friendship**
This schema defines a matrix where the cell value is the number of friends  and
have in common (as in Gilbert & Karahalios 2009; He et al. 2012),
```{r mutual_friends}
count_mutual_friends <- function(id_i, id_j, friends){
  length(intersect(
  # sets of friend ids
    friends$fbid[friends$id == id_i],
    friends$fbid[friends$id == id_j]
  ))
}

@@

**Network Overlap**
This schema defines a matrix where the cell value is the relative overlap of
each  pair’s social network (as in Adamic & Adar 2003),
```{r network_overlap}
calculate_newtork_overlap <- function(id_i, id_j, friends){
  mutual <- length(intersect( 
    # sets of friend ids
    friends$fbid[friends$id == id_i],
    friends$fbid[friends$id == id_j]
  ))

@@

**Direct Network Overlap**
This schema is similar to the Network Overlap, except that we give a bonus to
pairs that are themselves friends,
```{r direct_network_overlap}
friend_connections <- friend_connections %>%
  mutate( direct_overlap = overlap + direct )
```

>>>>

Candidate Weighting Schema
-----------------------------------------
The social network data we retrieved from Facebook allow us to construct four social weights matrices, which we describe in this section. To aid this presentation, we must first establish some basic notation following elementary set theory. The set of friends of an individual $i$ is defined as $\phi_i$. The cardinality of this set is the number of friends, so therefore the quantity $|\phi_i \cup \phi_j|$ represents the number of friends that individuals $i$ and $j$ have in common.

```{r connections_frame}
friend_connections <- tbl_df(expand.grid(id_i = user$id, id_j = user$id)) %>%
  group_by(id_i, id_j)
```

@@

friend_connections <- friend_connections %>%
  mutate(direct = check_friends(id_i, id_j, user, friends))
```

**Mutual Friendship**
This schema defines a matrix where the cell value is the number of friends  and
have in common (as in Gilbert & Karahalios 2009; He et al. 2012),

$$ w_{ij} = |\phi_i \cup \phi_j| $$

```{r mutual_friends}
count_mutual_friends <- function(id_i, id_j, friends){
  length(intersect(
  # sets of friend ids
    friends$fbid[friends$id == id_i],
    friends$fbid[friends$id == id_j]
  ))
}

@@

**Network Overlap**
This schema defines a matrix where the cell value is the relative overlap of
each pair’s social network (as in Adamic & Adar 2003),

$$ w_{ij} = \frac{|\phi_i \cup \phi_j|} {|\phi_i \cap \phi_j|} $$

```{r network_overlap}
calculate_newtork_overlap <- function(id_i, id_j, friends){
  mutual <- length(intersect( 
    # sets of friend ids
    friends$fbid[friends$id == id_i],
    friends$fbid[friends$id == id_j]
  ))

@@

**Direct Network Overlap**
This schema is the sum of the network overlap and direct friends schemata:

$$ w_{ij} =
  \begin{cases}
    \frac{|\phi_i \cup \phi_j|} {|\phi_i \cap \phi_j|} + 1 & 
      \text{if } i \in \phi_j \\
    \frac{|\phi_i \cup \phi_j|} {|\phi_i \cap \phi_j|}      & 
      \text{if } i \notin \phi_j
  \end{cases} $$

```{r direct_network_overlap}
friend_connections <- friend_connections %>%
  mutate( direct_overlap = overlap + direct )
```
